---
title: "PSY 8712 Week 8 Project"
author: "Evan Knep"
date: "`r Sys.Date()`"
output: html_document
---

# **Reproducible Image and Online Resources**

An image of this project as of *`r Sys.Date()`* can be accessed by [clicking this link](https://mybinder.org/v2/gh/evanknep/psy8712-week8/HEAD). 

An interactive web app is available by [clicking this link](https://knepx001.shinyapps.io/shiny_week8/) instead. 

# **Script Settings and Resources**
```{r script settings, echo=TRUE, results='hide', message=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
library(dplyr)
library(DT)
library(ggplot2)
```

# **Data Import and Cleaning**
Importing our dataset for preprocessing. Steps include reverse coding question q5 and converting our time columns into POSIX format. 

```{r data import and cleaning}
week8_tbl = read_csv("../data/week3.csv") %>% #initial data import
  mutate(q5 = 6 - q5) %>% #reverse coding our q5
  mutate(timeStart = as.POSIXct(timeStart)) %>% #converting our timestart and timeend columns to date time format
  mutate(timeEnd = as.POSIXct(timeEnd))
```
# **Visualization**
Presenting questionnaire scores in table format to allow access to raw scores, as well as a visualization of the relationship between questions 1-6 and and questions 8-10 via a correlation of the mean scores. Question 5 has been reverse scored. 
```{r visualization, echo=FALSE, message=FALSE}
week8_tbl %>%
  select(q1:q6) %>% #selecting our desired subset of questions
  DT::datatable(options = list(pageLength = 5)) # creating a table with paginations

week8_tbl %>%
  rowwise() %>%
  mutate(q1_q6_mean = mean(c_across(q1:q6), na.rm = TRUE),
         q8_q10_mean = mean(c_across(q8:q10), na.rm = TRUE)) %>%
  ggplot(aes(x=q1_q6_mean, y=q8_q10_mean)) + geom_point() + geom_smooth(method = "lm", color = "purple") + labs(x = "q1-q6 mean", y = "q8-q10 mean")


```

# **Analysis**
Observing the relationship between between responses to questions 1-6 and 8-10 by observing strength of correlation between the means of each batch of questions. 
```{r}
mean_scores_tbl <- week8_tbl %>% # I realize rerunning this same code from above is probably not the correct answer, but when I attempt to save a new tibble with the mean values all in a single pipeline it also contains the plotting information so it gets a bit weird
  rowwise() %>%
  mutate(q1_q6_mean = mean(c_across(q1:q6), na.rm = TRUE),
         q8_q10_mean = mean(c_across(q8:q10), na.rm = TRUE))

corr_values = cor.test(mean_scores_tbl$q1_q6_mean, mean_scores_tbl$q8_q10_mean)
```

When comparing the mean values of responses to questions 1-6 and 8-10, I find a correlation of `r corr_values$estimate`. Our p-value for this correlation is `r corr_values$p.value`, which when combined with our correlation of near 0, suggests that mean responses of questions 1-6 and 8-10 are not correlated. 

# **Data Export**

```{r Data Export}
mean_scores_tbl %>%
  select(-c(timeStart, condition, q1:q10)) %>%
  write_csv("../data/week8_shiny_data.csv")
```

